### 2024-04-12 introduction.tex
new intro

Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. In the era of complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks. This is where advanced simulation techniques, particularly nested simulation procedures, become indispensable.

>>>>

% Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
% For complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks. 
% This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
% In constract to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial products with multiple sources of risk.

The realm of financial risk management is in a constant state of evolution, driven by the rapid advancement of financial technologies and the increasing complexity of financial products. Traditional risk management techniques, which often rely on linear assumptions and static models, are increasingly inadequate for addressing the multifaceted and dynamic risks associated with modern financial instruments like variable annuities and derivatives portfolios. This thesis introduces cutting-edge machine learning approaches to enhance risk estimation and management, offering substantial improvements over conventional methods such as nested simulations.

Financial markets today are characterized by high volatility and intricate dependencies, influenced by global economic factors and interlinked financial systems. In such an environment, the ability to accurately estimate and hedge against potential risks is paramount. Traditional risk assessment methods, including standard nested simulations, often lack the flexibility and scalability required to handle the stochastic nature of modern financial markets. They also tend to be computationally intensive and can fail to capture extreme events, leading to substantial misestimations of risk and inadequate hedging strategies.

Recognizing these challenges, this research focuses on the application of machine learning models as metamodels within nested simulations. Machine learning offers the potential to automate and improve the accuracy of risk predictions, adapt to new patterns in data, and handle high-dimensional spaces efficiently. The adaptive nature of these models allows for better handling of the non-linear and time-varying patterns typical of financial markets, thus providing a more robust framework for risk assessment and decision-making.

The thesis is structured into three main sections, each addressing a different aspect of risk management through the lens of machine learning: The first section provides a comprehensive review of existing nested simulation techniques and introduces the concept of using machine learning models as metamodels. It compares various machine learning approaches, such as neural networks and ensemble methods, to traditional models, assessing their efficacy and efficiency in simulating tail risks. This comparison is foundational, setting the stage for the subsequent application of specific machine learning techniques to complex financial risk estimation tasks.

The second section details the implementation of Long Short-Term Memory (LSTM) networks to enhance the efficiency and accuracy of nested simulations in estimating the tail risk of variable annuities. By leveraging LSTMs, the research demonstrates significant improvements in computational speed and prediction accuracy. The ability of LSTM networks to process sequences of data and remember long-term dependencies makes them particularly suited for modeling the sequential risks associated with financial instruments over time.

The final section explores a novel approach to hedging variable annuities using a combination of Proximal Policy Optimization (PPO) and LSTM networks. This model-free reinforcement learning strategy adapts to changes in market conditions in real-time, providing a flexible and powerful tool for managing financial risks. The use of PPO, known for its stability and effectiveness in various control tasks, underscores the innovative aspect of this research, pushing the boundaries of how machine learning can be utilized in financial risk management.

This research aims not only to demonstrate the practical applications of machine learning in financial risk management but also to contribute to the theoretical advancement of risk management strategies. By bridging the gap between traditional financial models and modern machine learning techniques, this thesis provides valuable insights that could influence future practices and research in the field. The findings could have significant implications for both financial theorists and practitioners, pointing the way toward more resilient and adaptive financial systems.
